Rapid-response Bayesian sky localization for electromagnetic follow-up of gravitational-wave candidates

### 2013-02-12 ms.tex
New introduction for Fisher matrix section

\marginpar{Bad to start a paragraph with a citation number. Perhaps switch to natbib and use a \texttt{citet}-style reference. Keep this derivation as short as possible. Refer more directly to \cite{fairhurst:2009}. Tighten up notation as much as possible while still giving a concise description of the Cram\`er-Rao bound.}%
%
\cite{fairhurst:2009} estimated the uncertainty in the matched-filter measurement of the \ac{TOA} of a \ac{GW} signal by computing the scalar Fisher information. We extend this result by computing the Fisher information matrix describing the uncertainties in the joint estimation of the signal amplitude and \ac{TOA}.

>>>>

The \ac{CRLB} is a useful analytical tool for predicting with what error an unknown parameter or parameters can be estimated from noisy observations. When an unbiased estimator exists, the \ac{CRLB} bound says that the covariance of the estimation error is bounded below by the Fisher information matrix. The \ac{CRLB} has been widely applied in \ac{GW} astronomy, for instance by \cite{fairhurst:2009} to predict the sky localization accuracy that is achievable with \ac{GW} observations. Here, we review the Fisher matrix calculation in \cite{fairhurst:2009} but add some physical interpretation to the particular structure of the covariance matrix.
